---
title: "P8105 - Plotly & Dashboards"
output: 
  html_document:
    toc: true
    toc_float: true
---

### Load packages and data

```{r library, message = FALSE}
library(tidyverse)
library(p8105.datasets)
library(plotly)
```

```{r airbnb data}
data(nyc_airbnb) # This is a big dataset ~ 40,000 data, we need to sample down 

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(rating = review_scores_location / 2) %>%
  # I am making 10 stars to become 5 stars and so on..
  select(
    borough = neighbourhood_group, neighbourhood, rating, price, room_type, lat, long) %>%
  filter(
    !is.na(rating), # drop any rows that don't have any ratings.
    # we are narrowing down to only Manhattan, entire home/apt, & price range within 100-500.
    borough == "Manhattan", 
    room_type == "Entire home/apt",
    price %in% 100:500)
```

### Plotly allows us to interact with the plots!

```{r scatterplot}
nyc_airbnb %>% 
  mutate(
    text_label = str_c("Price: $", price)) %>% 
  plot_ly(
    x = ~lat, y = ~long, color = ~price,  
    type = "scatter", mode = "markers",
    alpha = 0.5, text = ~text_label)
```

```{r boxplot, warning = FALSE}
nyc_airbnb %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  plot_ly(
    y = ~price, color = ~neighbourhood,
    type = "box")
```

```{r bar plot, warning = FALSE}
nyc_airbnb %>% 
  count(neighbourhood) %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) %>% 
  plot_ly(
    x = ~neighbourhood, y = ~n, color = ~neighbourhood,
    type = "bar")
```


## Not recommend doing `ggplotly`

```{r ggplotly}
airbnb_scatter =
  nyc_airbnb %>% 
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point()

ggplotly(airbnb_scatter)
```


## Create a dashboard

Create a new Rmd file > From template > Flex Dashboard

If we save the `Dashboard.Rmd` file together with the Rproj, it will render the dashboard as a regular markdown document, but doesn't treat it as a dashboard.

There are two ways to fix this issue:
1. build the entire website
2. In console, type `rmarkdown::render("Dashboard.Rmd", output_format = "flexdashboard::flex_dashboard")` 



